---
title: "For the Longest Time: Continuity and Change in One Teaching-Related Subreddit"
author: "K. Bret Staudt Willet & Jeffrey P. Carpenter"
date: "01/24/2020"
output:
  pdf_document:
    toc: yes
  html_document:
    float_toc: yes
    toc: yes
---

# Get set up

This section loads the data and packages and starts to process the data, but doesn't calculate any statistics or create any results.

1. Load packages

```{r, include=FALSE}
library(knitr)
library(kableExtra)
library(tidyverse)  # for data manipulation
library(anytime)
library(lubridate)  # for working with dates
library(igraph)  # for processing the social network
library(ggraph)  # for visualizing the social network
```

2. Set up settings for sharing 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
usethis::use_git_ignore(c("*.csv", "*.rds", "*.log"))
```

3. Set timeframe

```{r timeframe, include=FALSE}
date_start <- as_datetime("2016-01-01 05:00:00 UTC") %>% 
        ymd_hms() %>%
        with_tz(tzone="US/Eastern")
date_end <- as_datetime("2019-07-01 03:59:59 UTC") %>% 
        ymd_hms() %>%
        with_tz(tzone="US/Eastern")
```

4. Load subreddit posts

```{r posts, include=FALSE}
posts_teachers <- read.csv("data/r-teachers-posts.csv", 
                            header=TRUE, 
                            colClasses='character'
                            ) %>%
        as.data.frame() %>%
        rename(post_id = id, 
               post_author = author,
               post_voting_score = score,
               post_text = selftext
               ) %>%
        mutate(post_date_time = created_utc %>% 
                       as.numeric() %>% 
                       anytime(asUTC=TRUE) %>% 
                       as_datetime %>%
                       ymd_hms() %>%
                       with_tz(tzone="US/Eastern"),
               post_voting_score = post_voting_score %>% as.numeric(),
               post_year = year(post_date_time),
               post_semester = semester(post_date_time, with_year=TRUE),
               post_word_count = str_count(title, "\\s+") + 
                       str_count(post_text, "\\s+") + 2
               ) %>%
        distinct(post_id, .keep_all = TRUE) %>%
        filter(post_date_time >= date_start,
               post_date_time <= date_end,
               post_id != "",
               !is.na(post_id),
               post_author != "",
               post_author != "[deleted]",
               post_text != "[deleted]",
               post_text != "[removed]"
               )
```

5. Load subreddit responses

```{r responses, include=FALSE}
responses_teachers <- read.csv("data/r-teachers-responses.csv", 
                            header=TRUE, 
                            colClasses='character'
                            ) %>%
        as.data.frame() %>% 
        rename(response_id = id, 
               response_author = author,
               response_voting_score = score,
               response_text = body) %>%
        mutate(thread_id = str_remove(link_id, pattern="t[0-9]_"),
               parent_id = str_remove(parent_id, pattern="t[0-9]_"),
               response_date_time = created_utc %>% 
                       as.numeric() %>% 
                       anytime(asUTC=TRUE) %>% 
                       as_datetime %>%
                       ymd_hms() %>%
                       with_tz(tzone="US/Eastern"),
               post_id = thread_id,
               response_voting_score = response_voting_score %>% as.numeric(),
               response_year = year(response_date_time),
               response_semester = semester(response_date_time, with_year=TRUE),
               response_word_count = str_count(response_text, "\\s+") + 1
               ) %>% 
        distinct(response_id, .keep_all = TRUE) %>%
        filter(response_date_time >= date_start,
               response_date_time <= date_end,
               response_id != "",
               !is.na(response_id),
               response_author != "",
               response_author != "[deleted]",
               response_text != "[deleted]",
               response_text != "[removed]"
               )
```

6. Load subreddit subscriber history

```{r subscribers, include=FALSE}
subreddit_subscribers <- read.csv("data/r-teachers-subscriber-history.csv", 
                            header=TRUE, 
                            colClasses='character'
                            ) %>%
        as.data.frame() %>%
        mutate(semester_mid = as.numeric(Period.Midpoint),
               semester = Semester) %>%
        select(semester, semester_mid) %>%
        filter(!is.na(semester_mid))
```

7. Create a merged dataframe of posts and responses for both subreddits.

```{r merged, include=FALSE}
merged_teachers <- posts_teachers %>% 
        left_join(responses_teachers, by=c('post_id')) %>%
        mutate(self_response = ifelse(is.na(response_author), 
                                      FALSE,
                                      ifelse(post_author==response_author, TRUE, FALSE)
                                      )
               ) %>%
        group_by(post_id) %>%
        mutate(n_responses = length(which(!is.na(response_id))),
               n_self_responses = length(which(self_response)), 
               p_self_responses = ifelse(n_responses==0, 
                                         0, 
                                         round(100 * n_self_responses / n_responses, 2)
                                         )
               ) %>%
        ungroup()
```

# Analysis and Results

## Figure 1. Contributions to r/Teachers and r/education each day from January 1, 2016 through June 30, 2019

```{r, include=TRUE, echo=FALSE}
n_months <- (date_end - date_start) %>% time_length(unit="months")

n_posts_overall_teachers <- length(unique(merged_teachers$post_id))

n_responses_overall_teachers <- merged_teachers %>%
        filter(., !is.na(response_id)) %>%
        pull(response_id) %>%
        unique() %>%
        length()
n_contributions_overall_teachers <- n_posts_overall_teachers +
        n_responses_overall_teachers
n_posters_overall_teachers <- length(unique(merged_teachers$post_author))

n_responders_overall_teachers <- merged_teachers %>%
        filter(., !is.na(response_author)) %>%
        pull(response_author) %>%
        unique() %>%
        length()
n_contributors_overall_teachers <- merged_teachers %>%
        c(pull(., post_author), pull(., response_author)) %>%
        unique() %>%
        length() -1  ## to account for the NA response_author

paste0("From the r/Teachers subreddit, we collected ", n_contributions_overall_teachers,  " contributions from ", n_contributors_overall_teachers, " contributors"); paste0("dated between ", date(date_start), " and ", date(date_end), " (", round(n_months, 2), " months),"); paste0("a total of ", n_posts_overall_teachers, " posts and ", n_responses_overall_teachers, " responses to those posts.")
```

```{r contributions-over-time-comparison, include=TRUE, echo=FALSE}
to_plot_posts_teachers <- posts_teachers$post_date_time %>% 
        floor_date("day") %>% 
        as_date() %>%
        table() %>% 
        as.data.frame() %>%
        rename(day = ".",
               n = Freq) %>%
        mutate(day = as_date(day),
               type = "post",
               subreddit = "teachers") %>%
        filter((day >= date_start) & (day <= date_end))
to_plot_responses_teachers <- responses_teachers$response_date_time %>% 
        floor_date("day") %>% 
        as_date() %>%
        table() %>% 
        as.data.frame() %>%
        rename(day = ".",
               n = Freq) %>%
        mutate(day = as_date(day),
               type = "response",
               subreddit = "teachers") %>%
        filter((day >= date_start) & (day <= date_end))
to_plot <- to_plot_posts_teachers %>% 
        full_join(to_plot_responses_teachers, by = c("subreddit", "day", "type", "n")) %>%
        mutate(subreddit = as.factor(subreddit),
               type = as.factor(type)
               )

ggplot(data = to_plot, mapping = aes(x=day, y=n, shape=type)) +
        geom_point(size=3, alpha=.8, color="#63ACBE") + 
        scale_shape_manual(values = c(17, 3)) +
        geom_smooth(method='lm', se=FALSE, size=2, color="black") +
        scale_y_continuous(trans='log10') +
        xlab(NULL) +
        ylab("Number of Contributions") +
        theme_bw() +
        theme(panel.grid.major = element_line(color = "gray30"),
              panel.grid.minor = element_line(color = "gray90"),
              axis.title=element_text(size=28, family='serif'),
              axis.text=element_text(size=24, family='serif'),
              legend.position='bottom',
              legend.box = 'vertical',
              legend.box.background = element_rect(),
              legend.title=element_text(size=28, family='serif'), 
              legend.text=element_text(size=24, family='serif')
              ) +
        labs(shape='Type of Contribution:')
```

```{r, include=FALSE}
#ggsave("output/contributions-over-time.png", width = 16, height = 9)
```

```{r regression-line, include=TRUE, echo=FALSE}
## Print the slopes of the linear regressions:
post_fit_teachers <- to_plot %>% 
        filter(type=='post', subreddit=='teachers') %>% 
        lm(n ~ day, data = .)
post_slope_teachers <- post_fit_teachers$coefficients[[2]] %>% round(2)
post_slope_pval_teachers <- summary(post_fit_teachers)$coef[2,4] %>% round(8)

response_fit_teachers <- to_plot %>% 
        filter(type=='response', subreddit=='teachers') %>% 
        lm(n ~ day, data = .)
response_slope_teachers <- response_fit_teachers$coefficients[[2]] %>% round(2)
response_slope_pval_teachers <- summary(response_fit_teachers)$coef[2,4] %>% round(8)

paste0("For the r/Teachers subreddit, the slope of the `post` linear regression is ", post_slope_teachers, " (p=", post_slope_pval_teachers, "),"); paste0("and the slope of the `response` linear regression is ", response_slope_teachers, " (p=", response_slope_pval_teachers, ").")
```

## Table 1. Contributions to r/Teachers

```{r table1, include=TRUE, echo=FALSE}
## have to subtract 1 to account for NA rows for n_responders and n_contributors
table1_teachers <- merged_teachers %>%
        group_by(post_semester) %>% 
        summarize(n_posters_teachers = length(unique(post_author)),
                  n_responders_teachers = length(unique(response_author)) - 1, 
                  n_contributors_teachers = length(unique(c(post_author, 
                                                            response_author))) - 1
                  ) %>%
        rename(semester=post_semester) %>%
        mutate(period = ifelse(semester==2016.1, "2016-Jan-Jun",
                                 ifelse(semester==2016.2, "2016-Jul-Dec",
                                        ifelse(semester==2017.1, "2017-Jan-Jun",
                                               ifelse(semester==2017.2, "2017-Jul-Dec",
                                                      ifelse(semester==2018.1, "2018-Jan-Jun",
                                                             ifelse(semester==2018.2, "2018-Jul-Dec", 
                                                                    "2019-Jan-Jun"
                                                                    )
                                                             )
                                                      )
                                               )
                                        )
                                 )
               ) %>%
        mutate(subscribers = subreddit_subscribers$semester_mid[1:7],
               prop_contributing = round(100 * n_contributors_teachers / subscribers, 2)
               )
n_multiple_posts <- merged_teachers %>% 
        group_by(post_semester) %>% 
        count(post_author) %>%
        filter(n>1) %>% 
        summarize(multiple_posts = length(n))
n_multiple_responses <- merged_teachers %>% 
        filter(., !is.na(response_author)) %>%
        group_by(post_semester) %>% 
        count(response_author) %>%
        filter(n > 1) %>% 
        summarize(multiple_responses = length(n))
posts_per <- merged_teachers %>% 
        group_by(post_semester) %>% 
        count(post_author) %>% 
        summarize(mean_posts = round(mean(n), 2),
                  sd_posts = round(sd(n), 2),
                  max_posts = max(n)
                  )
responses_per <- merged_teachers %>% 
        filter(., !is.na(response_author)) %>%
        group_by(post_semester) %>% 
        count(response_author) %>% 
        summarize(mean_responses = round(mean(n), 2),
                  sd_responses = round(sd(n), 2),
                  max_responses = max(n)
                  )
table1 <- table1_teachers %>% 
        mutate(multiple_posts = round(100 * n_multiple_posts$multiple_posts 
                                      / n_posters_teachers, 2),
               multiple_responses = round(100 * n_multiple_responses$multiple_responses 
                                          / n_responders_teachers, 2),
               mean_posts = posts_per$mean_posts,
               sd_posts = posts_per$sd_posts,
               max_posts = posts_per$max_posts,
               mean_responses = responses_per$mean_responses,
               sd_responses = responses_per$sd_responses,
               max_responses = responses_per$max_responses
               ) %>%
        select(period, subscribers, n_contributors_teachers, n_posters_teachers, n_responders_teachers, 
               prop_contributing, multiple_posts, multiple_responses, 
               mean_posts, sd_posts, max_posts, mean_responses, sd_responses, max_responses)
table1_kable <- table1 %>% 
        knitr::kable(align='c',
                     col.names=c("Period", "Subscribers", "Contributors",
                                 "Posters", "Responders", "Proportion Contributing", 
                                 "Multiple Posts", "Multiple Responses",
                                 "Posts/poster", "(SD)", "Max posts",
                                 "Responses/responder", "(SD)", "Max responses"
                                 )
                     ) %>% 
        kable_styling(c("striped", "bordered"))
#save_kable(table1_kable, "output/table1.png")  # requires webshot::install_phantomjs()
table1_kable
```

## Table 2. Content Interaction in r/Teachers

```{r table2, include=TRUE, echo=FALSE}
## have to subtract 1 to account for NA rows for n_threads and n_responses
table2_teachers <- merged_teachers %>% 
        group_by(post_semester) %>% 
        summarize(n_posts_teachers = length(unique(post_id)),
                  n_threads_teachers = length(unique(thread_id)) - 1,
                  n_responses_teachers = length(unique(response_id)) - 1,
                  n_nonzero_teachers = n_posts_teachers - length(which(is.na(response_text))),
                  words_per_post = round(mean(post_word_count), 2),
                  words_per_response = round(mean(response_word_count, na.rm=TRUE), 2),
                  mean_post_voting = round(mean(post_voting_score), 2),
                  mean_response_voting = round(mean(response_voting_score, na.rm=TRUE), 2)
                  ) %>%
        mutate(response_rate_teachers = round((100 * n_nonzero_teachers / n_posts_teachers), 2),
               responses_per_thread_teachers = round((n_responses_teachers / n_threads_teachers), 2)
               ) %>%
        rename(semester=post_semester) %>% 
        mutate(period = ifelse(semester==2016.1, "2016-Jan-Jun",
                                 ifelse(semester==2016.2, "2016-Jul-Dec",
                                        ifelse(semester==2017.1, "2017-Jan-Jun",
                                               ifelse(semester==2017.2, "2017-Jul-Dec",
                                                      ifelse(semester==2018.1, "2018-Jan-Jun",
                                                             ifelse(semester==2018.2, "2018-Jul-Dec", 
                                                                    "2019-Jan-Jun"
                                                                    )
                                                             )
                                                      )
                                               )
                                        )
                                 )
               ) %>%
        select(period, 
               n_posts_teachers, n_threads_teachers, n_responses_teachers, 
               response_rate_teachers, responses_per_thread_teachers,
               words_per_post, words_per_response, 
               mean_post_voting, mean_response_voting)
table2_kable <- table2_teachers %>% 
        knitr::kable(align='c',
                     col.names=c("Period", "Posts", "Threads", "Responses",
                                 "Response Rate", "Responses per Thread",
                                 "Words per Post", "Words per Response",
                                 "Post Votes", "Response Votes")
                     ) %>% 
        kable_styling(c("striped", "bordered"))
#save_kable(table2_kable, "output/table2.png")  # requires webshot::install_phantomjs()
table2_kable
```

## Table 3. Social Interaction in r/Teachers

```{r table3, include=TRUE, echo=FALSE}
## retrieve the name of the parent author, create edgelist, and then build the network graph
network_graph_teachers <- merged_teachers %>%
        filter(parent_id %in% c(posts_teachers$post_id, 
                                         responses_teachers$thread_id, 
                                         responses_teachers$response_id)) %>%
        mutate(parent_author = ifelse(parent_id %in% merged_teachers$post_id,
                                      post_author,
                                      response_author
                                      )
               ) %>% 
        group_split(post_semester) %>%
        lapply(., function(x) {
                as.data.frame(x) %>% 
                        select(response_author, parent_author)%>%
                        as.matrix() %>%
                        graph_from_edgelist(directed=TRUE) %>% 
                        set_vertex_attr(name='degree', value=degree(., mode='total', loops=FALSE))
                }
               )

nodes_teachers <- sapply(network_graph_teachers, function(x) {length(V(x))})
edges_teachers <- sapply(network_graph_teachers, gsize)
transitivity_teachers <- sapply(network_graph_teachers, transitivity) %>% round(4)
reciprocity_teachers <- sapply(network_graph_teachers, reciprocity) %>% round(4)

degrees_teachers_list <- lapply(network_graph_teachers, function(x) {vertex_attr(x, name='degree')})
names(degrees_teachers_list) <- c("2016-Jan-Jun", "2016-Jul-Dec",
                                  "2017-Jan-Jun", "2017-Jul-Dec",
                                  "2018-Jan-Jun", "2018-Jul-Dec", 
                                  "2019-Jan-Jun")
degrees_teachers_df  <- map_df(degrees_teachers_list, ~ as.data.frame(.x), .id='period') %>%
        rename(degree_teachers = .x) %>%
        group_by(period) %>%
        summarize(degree_mean = round(mean(degree_teachers), 2),
                  degree_sd = round(sd(degree_teachers), 2),
                  degree_median = median(degree_teachers),
                  degree_min = min(degree_teachers),
                  degree_max = max(degree_teachers)
                  )

table3_teachers <- degrees_teachers_df %>% 
        cbind(nodes_teachers) %>%
        cbind(edges_teachers) %>%
        cbind(transitivity_teachers) %>%
        cbind(reciprocity_teachers) %>%
        select(period, nodes_teachers, edges_teachers, 
               transitivity_teachers, reciprocity_teachers,
               degree_mean, degree_sd, degree_median, degree_min, degree_max
               )

table3_kable <- table3_teachers %>% 
        knitr::kable(align='c',
                     col.names=c("Period", "Nodes", "Edges",
                                 "Transitivity", "Reciprocity", 
                                 "Mean", "SD", "Median", "Min", "Max")
                     ) %>% 
        kable_styling(c("striped", "bordered")) %>%
        add_header_above(c(" " = 5, "Node Degree" = 5))
#save_kable(table3_kable, "output/table3.png")  # requires webshot::install_phantomjs()
table3_kable
```

# Version/dependencies

```{r, session-info}
sessionInfo()
```